Plot Figures for McDuffie et al., 2023 (those generated in R)

### 2023-05-11 analysis/Manuscript/Paper_RFigures.Rmd
Added pop/mort pre-processing scripts & data

#IF Data on ratios of respiratory to total mortality rates
IFsFactors<-read.csv(file.path(inputs,'IFP',"adjustment_factors.csv"))  
IFsCountry<-read.csv(file.path(inputs,'IFP',"country_codes.csv"))
  names(IFsCountry)[1] <- 'RegionName2'
IFsCtryCross<-read.csv(file.path(inputs,'IFP',"country_crosswalk.csv"))
IFsFactors<-left_join(IFsFactors,IFsCountry,by=c("Region"="RegionNum"))
IFsFactors<-left_join(IFsFactors,IFsCtryCross,by=c("RegionName2"="IFsName"),multiple='all')
  names(IFsFactors)<-c("X","Years","Region","RFF_Age_range","final_AF",
                       "RegionName","LocID","RFFName","Notes")
IFsFactors<-IFsFactors[,2:8]
Cross.year<-read_xlsx(file.path(inputs,'IFP','Crosswalk RFF Mort Year.xlsx'))
mean.pop<-read.csv(file.path(inputs,'RFF',"rff_pop_means.csv"))
#subset for relevant years (<2100)
mean.pop<-mean.pop[(mean.pop$Year<=2100),]
mean.pop <- mean.pop %>%
  filter(Year <= 2100) %>%
  mutate(mean_pop = mean_pop *1000) #convert to ppl counts

>>>>

#IF Data on ratios of respiratory to total mortality rates
IFsFactors<-read.csv(file.path(inputs3,'IFP',"adjustment_factors.csv"))  
IFsCountry<-read.csv(file.path(inputs3,'IFP',"country_codes.csv"))
  names(IFsCountry)[1] <- 'RegionName2'
IFsCtryCross<-read.csv(file.path(inputs3,'IFP',"country_crosswalk.csv"))
IFsFactors<-left_join(IFsFactors,IFsCountry,by=c("Region"="RegionNum"))
IFsFactors<-left_join(IFsFactors,IFsCtryCross,by=c("RegionName2"="IFsName"),multiple='all')
  names(IFsFactors)<-c("X","Years","Region","RFF_Age_range","final_AF",
                       "RegionName","LocID","RFFName","Notes")
IFsFactors<-IFsFactors[,2:8]
Cross.year<-read_xlsx(file.path(inputs3,'IFP','Crosswalk RFF Mort Year.xlsx'))
mean.pop<-read.csv(file.path(inputs,'RFF',"rff_pop_means.csv"))
#subset for relevant years (<2100)
mean.pop<-mean.pop[(mean.pop$Year<=2100),]
mean.pop <- mean.pop %>%
  filter(Year <= 2100) %>%
  mutate(mean_pop = mean_pop *1000) #convert to ppl counts
